---
title: "test_clwcmap"
author: "Anna"
date: "2026-02-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
library(tidyverse)
library(ggmap)
library(ggsci)
library(leaflet)
library(ggthemes) 
library(RColorBrewer)
library(janitor)
library(readr)
library(googlesheets4)
library(stringr)
#knitr::opts_chunk$set(tidy = FALSE, message=FALSE, warning=FALSE)
```

##Import the data


```{r}

#data <- read_csv("~/Downloads/Central Community Impact Data Repository - Sheet2(3).csv", col_names = TRUE, show_col_types = FALSE)

data <- read_csv("~/Downloads/Central Community Impact Data Repository - Sheet2(3).csv", 
                 col_names = c("Time", "is_resident", "volunteer_name", "comment_source", "comment_date", "time_of_comment", "source_context", "resident_name", "name_consent", "incident_location", "comment_consent", "location_consent", "timing_extras", "incident_start_date", "incident_time", "all_harms", "personal_comment", "wind direction", "sand_mine_location", "if_photos", "photo_links", "photo_links2", "can_we_reach_out", "if_clwc_maling","incident_end_date", "weather", "sand_mine_owners", "certify", "email", "phone number"), show_col_types = FALSE)

```


```{r}
#data2<- read_sheet('https://docs.google.com/spreadsheets/d/1wrzd1ANfwNCgrm3WCnBL_qYAf0PtrrUBOlttzm8SSxs/edit?resourcekey=&gid=1791295176#gid=1791295176')

data <- read_csv("Central Community Impact Data Repository - Sheet2.csv", 
    col_types = cols(Timestamp = col_datetime(format = "%m/%d/%Y %H:%M:%S"), 
        `What date did you receive the comment?` = col_date(format = "%m/%d/%Y"), 
        `What time did you receive the comment?` = col_character(), 
        `Start date of the incident?` = col_date(format = "%m/%d/%Y"))
)
#col_factor(levels = c("No", "Yes", "No (we will write //"anonymous

#`Are you a resident submitting personal community comment?` = col_factor(levels = c("No, I am a volunteer submitting comment from another source", "Yes"))

data2<-data |>
  janitor::clean_names()

#or read_sheet. 
```

## Data tidying
```{r}
#divide all_harms into individual columns
impacts <- data[-1, ] |>

  mutate(Sand_on_property = str_detect(all_harms, "Sand on property")) |>
  mutate(Airborne_Sand = str_detect(all_harms, "Airborne Sand")) |>
  mutate(Personal_Health = str_detect(all_harms, "Personal Health")) |>
  mutate(Noise = str_detect(all_harms, "Noise")) |>
  mutate(Truck_Traffic = str_detect(all_harms, "Truck Traffic")) |>
  mutate(Safety_concern = str_detect(all_harms, "Safety Concern")) |>
  mutate(Sedimentation = str_detect(all_harms, "Harm to wildlife"))


Pivot_longer(impacts, cols, names_to = "name", values_to = "value", values_drop_na = FALSE 

```

```{r}
#could change the data in this way
#levels(data2$may_we_post_your_name_on_the_community_dashboard) <- list("No_anon" = c('No', 'No (we will write "anonymous")'))

#this coupld work
data_3<- data2 |>
    mutate(may_we_post_name = str_replace(may_we_post_your_name_on_the_community_dashboard, "No-anon"= "No"))

           
```

Find a dataset that is related to your project topic but not built into `R`. Load the data into `R`, make sure it is clean, and construct one interesting visualization of the data. Each project team member should find a different data set.

#work on parsing the addresses (manually)
  (with chatgpt)
```{r}
#
#location <- data2$what_is_location_of_the_incident_you_are_reporting_please_include_exact_address

pattern <- "^([:alnum:]*?)*(?=\\b(Carver|Plymouth)\\b)"

#pattern <- "^(.*?[^[:space:][:punct:]])(?=\\s*\\b(Carver|Plymouth)\\b)"

data3<-data2 |>
mutate(location_report = str_extract(what_is_location_of_the_incident_you_are_reporting_please_include_exact_address, pattern))
#mutate(location_report2 = str_extract, location_report()

```

```{r}
x

```


#take clean-ish addresses and provide codes
```{r}
install.packages('tidygeocoder')
library(tidygeocoder)

data3$incident_location <- data3$what_is_location_of_the_incident_you_are_reporting_please_include_exact_address


data4 <- data3 %>%
  geocode(incident_location, method = 'osm', lat = latitude , long = longitude)
```

```{r}
#pallate2 <- colorNumeric(palette = c("#0868ac", "#fecc5c", "#fd8d3c", "#f03b20", "#bd0026") , domain = departures2$pct_casual)

library (leaflet)

leaflet(data4) %>%
  addTiles() %>% 
  addProviderTiles(providers$CartoDB.Positron)%>%
  addCircles(data = data4,
             lng = ~longitude, 
             lat =  ~latitude, 
             radius = 4,
            # color = ~pallate2(pct_casual),
            # label = ~count, 
             # label = ~paste("departures/day",": ", round(count, 2), sep=""))
             popup = ~paste("incident date"), ") %>% 
```


## Plotting example!! 

here is the leaflet plot example

```{r, fig.caption = "DC bikemap", echo=FALSE }
pallate2 <- colorNumeric(palette = c("#0868ac", "#fecc5c", "#fd8d3c", "#f03b20", "#bd0026") , domain = departures2$pct_casual)
#"YlOrRd"
#c("#fecc5c", "#fd8d3c", "#f03b20", "#bd0026")

leaflet(departures2) %>%
  addTiles() %>% 
  addProviderTiles(providers$CartoDB.Positron)%>%
  addCircles(data = departures2,
             lng = ~long, 
             lat =  ~lat, 
             radius = 4, # ~variable ... or add circle markers? * multiply by a constant. 
             color = ~pallate2(pct_casual),
            # label = ~count, 
             label = ~paste("departures/day",": ", round(count, 2), sep="")) %>% 
             #popup = ~paste("departures/day",": ", round(count, 2), sep="")) %>% 
            
  #popup is upon click, label is hovering
            
  # Add a legend
  addLegend(pal = pallate2, 
            values = ~pct_casual, 
            opacity = 1, 
            title ="Percentage of Casual Users",
            position = "topleft") 


```

# Data table interactive
```{r}
#use DT package
```


