---
title: "test_clwcmap"
author: "Anna and joe!!"
date: "2026-02-24"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
library(tidyverse)
library(ggmap)
library(ggsci)
library(leaflet)
library(ggthemes) 
library(RColorBrewer)
library(janitor)
library(stringr)
library(readr)
library(googlesheets4)
library(dplyr)

library(httr2) # for accessing API for weather data
library(tidygeocoder)
library(plotly)
#plotting libraries
library(leaflet)
library(leaflet.extras2)

```


#reading in the data
```{r}
data <- read_sheet('https://docs.google.com/spreadsheets/d/1wrzd1ANfwNCgrm3WCnBL_qYAf0PtrrUBOlttzm8SSxs/edit?resourcekey=&gid=1791295176#gid=1791295176', sheet = 2) 

```

# load plymouth weather data
```{r}
get_openmeteo_wind <- function(lat, lon, start_date, end_date, tz = "America/New_York") {
  
  resp <- request("https://archive-api.open-meteo.com/v1/archive") |>
    req_url_query(
      latitude              = lat,
      longitude             = lon,
      start_date            = as.character(start_date),
      end_date              = as.character(end_date),
      hourly                = "wind_speed_10m,wind_gusts_10m",
      wind_speed_unit       = "mph",
      timezone              = tz
    ) |>
    req_perform() |>
    resp_body_json()
  
  data.frame(
    date                   = as.POSIXct(unlist(resp$hourly$time), format = "%Y-%m-%dT%H:%M", tz = tz),
    hourly_wind_speed      = unlist(resp$hourly$wind_speed_10m),
    hourly_wind_gust_speed = unlist(resp$hourly$wind_gusts_10m)
  )
}

# Usage
plym_weather_fresh <- get_openmeteo_wind(
  lat        = 41.9090,
  lon        = -70.7279,
  start_date = "2025-01-01",
  end_date   = Sys.Date()
)
```

# plot complaints recieved vs. ws
```{r}
incident_dates <- as.POSIXct(data$incident_start_date, format = "%Y-%m-%d %H:%M:%S", tz = "America/New_York")

incidents_weather <- plym_weather_fresh |>
  mutate(
    incident = map_lgl(.data$date, ~ any(abs(difftime(.x, incident_dates, units = "mins")) <= 30))
  )

winds<- ggplot(filter(plym_weather_fresh), aes(x = date)) +
  geom_point(aes(y = hourly_wind_speed), size = .1)+
  geom_line(aes(y = hourly_wind_speed),linewidth = .01)+
  geom_point(aes(y = hourly_wind_gust_speed), size = 0.75, color = 'blue', shape = 3)+
  geom_point(
    data = filter(incidents_weather, incident),
    aes(x = date, y = hourly_wind_speed),
    color = "red", size = 5, shape = 21, fill = "red"
  ) +
  theme_classic()+
  labs(x = "Date",
       y = "Wind Speed (MPH)")

ggplotly(winds)
```


#data <- read_csv("Central Community Impact Data Repository - Sheet2.csv", 
        col_types = cols(Timestamp = col_datetime(format = "%m/%d/%Y %H:%M:%S"), 
        `What date did you receive the comment?` = col_date(format = "%m/%d/%Y"), 
        `What time did you receive the comment?` = col_character(), 
        `Start date of the incident?` = col_date(format = "%m/%d/%Y"))) |>
       janitor::clean_names()
       
       
```{r}
 # Define jitter amount (e.g., ~1km)
jitter_val <- 0.0072 # 0.0072 degrees is ~0.5 miles => the locations are randomized up to 1/2 mile from origin

#mutate the data
data <- data|>
      geocode(incident_location, method = 'osm', lat = lat , long = long)
```

#change the data based upon consent 
```{r}
data <- data |>
  mutate(lat2 = case_when(location_consent == "No" ~ lat + runif(n(), -jitter_val, jitter_val),
                             (location_consent == "Yes") ~ lat)) |>
  mutate(long2 = if_else(location_consent == "No", (long + runif(n(), -jitter_val, jitter_val)), long))|>
  mutate(name2 = case_when(name_consent == "Yes" ~ resident_name,
                           TRUE ~ "Anonymous")) |>
  mutate(comment2 = case_when(comment_consent == "Yes" ~ personal_comment,
                           TRUE ~ NA))


```


## Count of the individual impacts 
```{r}
impacts <- data|>
  select(sand_on_property:harm_to_wildlife)|>
  pivot_longer (cols = 1:7, names_to = "type_of_harm", values_to = "value", values_drop_na = FALSE) |>
  filter(value == TRUE)


ggplot(impacts, aes(x = type_of_harm, fill = type_of_harm))+
  geom_bar()

```

Plot the points:
```{r}


leaflet(data) %>%
  addTiles() %>% 
  #addProviderTiles(providers$CartoDB.Positron)%>% 
  addProviderTiles(providers$Esri.WorldImagery)%>% 
  addCircleMarkers(data = data,
             lng = ~long2, 
             lat =  ~lat2, 
             radius = 5,
             color = "#FFAC1C",
             popup = ~paste("<strong>Start Date:</strong> ", incident_start_date, "<br>",
                            "<strong>Harms Reported:</strong> ", harms_list, "<br>",
                            "<strong>Comment:</strong> ", comment2),
                          clusterOptions = markerClusterOptions()) %>%
  
  #originaldata 
   addCircleMarkers(data = data,
             lng = ~long, 
             lat =  ~lat, 
             radius = 5,
             color = "yellow") %>%
  markerClusterOptions(
      spiderfyOnMaxZoom = FALSE,
      disableClusteringAtZoom = TRUE) %>%  #I dont think this does anything...
  labelOptions(
    opacity = 1,
    textsize = "30px"
  )

```


```{r}
labelOptions(
  interactive = FALSE,
  clickable = NULL,
  noHide = NULL,
  permanent = FALSE,
  className = "",
  direction = "auto",
  offset = c(0, 0),
  opacity = 1,
  textsize = "10px",
  textOnly = FALSE,
  style = NULL,
  zoomAnimation = NULL,
  sticky = TRUE,
  ...
)

markerOptions(
  interactive = TRUE,
  clickable = NULL,
  draggable = FALSE,
  keyboard = TRUE,
  title = "",
  alt = "",
  zIndexOffset = 0,
  opacity = 1,
  riseOnHover = FALSE,
  riseOffset = 250,
  ...
)

markerClusterOptions(
  showCoverageOnHover = TRUE,
  zoomToBoundsOnClick = TRUE,
  spiderfyOnMaxZoom = TRUE,
  removeOutsideVisibleBounds = TRUE,
  spiderLegPolylineOptions = list(weight = 1.5, color = "#222", opacity = 0.5),
  freezeAtZoom = FALSE,
  ...
)
```

Note: you may be interested in disabling spiderfyOnMaxZoom option when using disableClusteringAtZoom.

## Plotting example!! 

here is the leaflet plot example

```{r, fig.caption = "DC bikemap", echo=FALSE }
pallate2 <- colorNumeric(palette = c("#0868ac", "#fecc5c", "#fd8d3c", "#f03b20", "#bd0026") , domain = departures2$pct_casual)
#"YlOrRd"
#c("#fecc5c", "#fd8d3c", "#f03b20", "#bd0026")

leaflet(departures2) %>%
  addTiles() %>% 
  addProviderTiles(providers$CartoDB.Positron)%>%
  addCircles(data = departures2,
             lng = ~long, 
             lat =  ~lat, 
             radius = 4, # ~variable ... or add circle markers? * multiply by a constant. 
             color = ~pallate2(pct_casual),
            # label = ~count, 
             label = ~paste("departures/day",": ", round(count, 2), sep="")) %>% 
             #popup = ~paste("departures/day",": ", round(count, 2), sep="")) %>% 
            
  #popup is upon click, label is hovering
            
  # Add a legend
  addLegend(pal = pallate2, 
            values = ~pct_casual, 
            opacity = 1, 
            title ="Percentage of Casual Users",
            position = "topleft") 


```

# Data table interactive
```{r}
#use DT package
```

#shiny app
see the testSandApp folder


